\tool: Revisiting BadUSB with Type-C

### 2021-03-17 WOOT/Files/experiment.tex

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' to switch between different modes for external display. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen. However, if the victim has default setting for external monitor display mode, \tool will have to try these keystroke repeatedly to set itself into mirroring the victim's screen. For example, in Ubuntu, if the default setting is to disable external screen, \tool needs to press `Win+P' four times while if the default setting is to extend the primary screen, \tool needs to press `Win+P' five times. In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.

>>>>

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for `Win' key) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar to Ubuntu. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen. \tool needs to press `Win+P' five times. In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.
		\begin{figure}[H]
			\includegraphics[width=\linewidth]{./Figs/ubuntu_switch.png}\\	
			\caption{Screen Mode Switch in Ubuntu.}
			\label{fig:ubuntu_switch}
		\end{figure}
